Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Fixing notation.

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[-k] \rightarrowtail
T$ and $P[-k] \hookrightarrow T$ respectively.

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and edges
    between vertices $p$ and $q$ if there are at least $n$ simple paths of length exactly $\ell$
    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[-k] \rightarrowtail
    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[-k]
    \rightarrowtail T^{n - k, 2}$.
\end{proposition}

>>>>

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[k] \rightarrowtail
T$ and $P[k] \hookrightarrow T$ respectively.

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and edges
    between vertices $p$ and $q$ if there are at least $n$ simple paths of length exactly $\ell$
    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[k] \rightarrowtail
    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[k]
    \rightarrowtail T^{n - k, 2}$.
\end{proposition}
